---
title: "AE-12 Zach Perry"
author: "Zachary Perry"
---

# Setup
```{r Loading-Packages}
library(tidyverse)
library(tidymodels)
library(schrute)
library(lubridate)
library(kableExtra)
set.seed(1234)
```

# Glimpsing theoffice dataset
```{r Glimpse-Dataset}
glimpse(theoffice)
```
# Fix air_date for later use.
```{r Fix-Air-Date}
theoffice <- theoffice %>%
  mutate(air_date = ymd(as.character(air_date)))

theoffice
```
# Exercise 1:
Calculate the percentage of lines spoken by Jim, Pam, Michael, and Dwight for each episode of The Office.
```{r E1}
office_lines <-
theoffice |>
  filter(character == c("Jim", "Pam", "Michael", "Dwight")) |>
  count(character) |>
  mutate(per = n/sum(n))
  
office_lines
```

# Exercise 2:
Identify episodes that touch on Halloween, Valentine's Day, and Christmas
```{r E2}

theoffice <- theoffice |>
  mutate(text = tolower(text))

halloween_episodes <-
theoffice |>
  filter(str_detect(text, "halloween")) |>
  count(episode_name) |>
  filter(n > 0) |>
  mutate(halloween = 1) |>
  select(-n)

Vday_episodes <-
theoffice |>
  filter(str_detect(text, "valentine's day")) |>
  count(episode_name) |>
  filter(n > 0) |>
  mutate(vday = 1) |>
  select(-n)

Christmas_episodes <-
theoffice |>
  filter(str_detect(text, "christmas")) |>
  count(episode_name) |>
  filter(n > 0) |>
  mutate(Christmas = 1) |>
  select(-n)

halloween_episodes
Vday_episodes
Christmas_episodes
```

# Exercise 3:
Put together a modeling dataset that includes features you've engineered. Also add an indicator variable called michael which takes the value 1 if Michael Scott (Steve Carell) was there, and 0 if not. Note: Michael Scott (Steve Carell) left the show at the end of Season 7.
```{r E3}

joined_theoffice <-
theoffice |>
  left_join(halloween_episodes, by = "episode_name") |>
  left_join(Vday_episodes, by = "episode_name") |> 
  left_join(Christmas_episodes, by = "episode_name") |>
  replace_na(list(halloween =0, Christmas = 0, vday = 0))

joined_theoffice <- joined_theoffice |>
  mutate(michael = if_else(season < 8,1,0))

joined_theoffice
```

# Exercise 4:
Split the data into training (75%) and testing (25%)
```{r E4}
set.seed(1122)
office_split <- initial_split(joined_theoffice)
office_train <- training(office_split)
office_test <- testing(office_split)
```


# Exercise 5:
```{r E5}
office_model <-
linear_reg() |>
  set_engine("lm")
office_model
```

# Exercise 6:
Create a recipe that updates the role of episode_name to not be a predictor, removes air_date as a predictor, and removes all zero variance predictors.
```{r E6}

office_recipe <-
recipe(imdb_rating~., data = office_train) |>
  update_role(episode_name, new_role = "id") |>
  step_rm(air_date)|>
  step_dummy(all_nominal(), -episode_name) |>
  step_zv(all_predictors())

office_recipe
```

# Exercise 7:
Build a workflow for fitting the model specified earlier and using the recipe you developed to preprocess the data.
```{r E7}
office_workflow <- workflow() %>%
  add_model(office_model) %>%
  add_recipe(office_recipe)
```

# Exercise 8:
Fit the model to training data and interpret a couple of the slope coefficients.
```{r E8}
#office_fit <- office_workflow %>%
#  fit(data = office_train)

#tidy(office_fit)
```


# Exercise 9:


















